### 2015-03-02 paper_10_intro.tex
work on chapter 5, SDLC-AE

>>>>

    Iqbal, Ureche, Hausenblas, and Tummarello introduced a methodology named
    Linked Data Driven Software Development (LD2SD) which is a collection
    of various software artifacts into linked data \cite{Iqbal2009}.  This
    is one of the original attempts to collect software engineering data.
    The methodology links version control, discussion forums, and issue tracking
    data. The result is web-scale integration of data, but the actual
    benefits are still uncertain.

### 2015-03-02 paper_50_sdlc-ae.tex
work on chapter 5, SDLC-AE

In order for an SDO to properly track the elements of CRI, a data storage system should be available to store the appropriate data.  A consistent storage system should help to avoid the problem of inaccurate
data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
is implemented correctly by allowing limited changes to existing data, it will be able to alleviate
some of the dishonesty that is currently present in software projects \cite{Rost2011}. This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.

Once all the SDLC data is collected into a single place, there are many possible applications.  Software analytics
will be much easier to create and gamification will be much more easily attainable.

\begin{figure}[ht]
\includegraphics[scale=.6]{images/sdlcae.png}
\caption{SDLC ANALYTIC ENGINE}
\label{fig:sdlc-ae}
\end{figure}

\subsection{DATABASE STRUCTURE}
   All the data necessary to compute CRI needs to be stored in a database.  This section will 
   lay out the structure of tables and relationships necessary to the store all the data
   within a relational database.

@@

        Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
        database tables for storing the raw CRI data.  The SQL is written for an Oracle
        database, but the scripts can be modified to work with another database
        such as: PostgreSQL, SQL Server, or MySQL.

    \subsubsection{INTERMEDIATE SCORE TABLES FOR CRI}

@@

    \subsubsection{FINAL SCORE TABLES FOR CRI}

@@

\subsection{QUERIES}
    The section will provide the necessary SQL queries to obtain the correct data
    needed to compute the individual elements of CRI.

\subsection{COMPUTATIONS}
    This section will provide R scripts to calculate each individual score and the overall 
    CRI score. The scripts will need to be run every time the data is updated and the CRI
    score needs to be recalculated.

making decisions based upon historical data. 
Data Driven Software Engineering not Data Driven Software Development

>>>>

    In order for an SDO to properly track the elements of CRI, a data storage 
    system should be available to store the appropriate data.  A consistent 
    storage system should help to avoid the problem of inaccurate
    data caused by numerous manipulations of the existing data 
    \cite{Olson2003}. Plus, if the system
    is implemented correctly by allowing limited changes to existing data, 
    it will be able to alleviate
    some of the dishonesty that is currently present in software projects 
    \cite{Rost2011}. This storage system will be named the SDLC Analytic 
    Engine (SDLC-AE).

    Once all the SDLC data is collected into a single place, there are 
    many possible applications.  Software analytics
    will be much easier to create and gamification will be much more easily attainable.  
    CRI is just one possible application of the SDLC-AE.  Figure \ref{fig:sdlc-ae} 
    provides an overview of 
    the data that could potentially be stored in the SDLC-AE as it relates to CRI. The
    SDLC-AE does not specify how the data is entered, just how the data is stored.

    \begin{figure}[ht]
        \includegraphics[scale=.75]{images/sdlcae.png}
        \caption{SDLC ANALYTIC ENGINE}
        \label{fig:sdlc-ae}
    \end{figure}

    \subsection{DATABASE STRUCTURE}
        All the data necessary to compute CRI needs to be stored in a database.  This section will 
        lay out the structure of tables and relationships necessary to the store all the data
        within a relational database.  The SQL\footnote{Structured Query Language (SQL) is 
        a programming language designed for managing data in relational database 
        management system.} 
        is written for an Oracle
        database, but the scripts can be modified to work with another database
        such as: PostgreSQL, SQL Server, or MySQL.

@@

            Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
            database tables for storing the raw CRI data.

        \subsubsection{INTERMEDIATE SCORE TABLES FOR CRI}
            The next set of tables that need to be created are for the 
            intermediate level element scores.  These tables hold the
            element scores at the application\_id, service\_id, and project\_id
            level.  Figure \ref{fig:score_tables} provides a visual overview
            of the necessary tables.  Furthermore, these tables also lack
            relationships between one another because at this point, all the
            element scores are still being treated independently.  The five
            table names are:

            \begin{enumerate}
                \item QUALITY\_SCORE
                \item AVAILABILITY\_SCORE
                \item SATISFACTION\_SCORE
                \item SCHEDULE\_SCORE
                \item REQUIREMENTS\_SCORE
            \end{enumerate}
            Again, these table names match very closely with the 5 elements of CRI.

@@

        \subsubsection{FINAL SCORE TABLES FOR CRI}
            The final set of tables consists of only two tables.  
            \begin{enumerate}
                \item ELEMENT
                \item CRI\_SCORE
            \end{enumerate}
            The first
            table is the ELEMENT table.  It simply stores the CRI element 
            (Quality, Availability,Satisfaction,Schedule,Requirements,Overall) and 
            optional description. The second table is the CRI\_SCORE table.  
            It stores all the final element scores and the final overall CRI
            score.  It is related to the ELEMENT table.  Figure 
            \ref{fig:final_score_tables} provides a visual representation of the 
            relationship between the 2 tables.

@@

%    \subsection{QUERIES}
%        The section will provide the necessary SQL queries to obtain the correct data
%        needed to compute the individual elements of CRI.
%        
%    \subsection{COMPUTATIONS}
%        This section will provide R scripts to calculate each individual score and the overall 
%        CRI score. The scripts will need to be run every time the data is updated and the CRI
%        score needs to be recalculated.

### 2015-03-02 paper_80_conclusion.tex
some minor typos and proof reading
adding some SDLC-AE diagrams
work on chapter 5, SDLC-AE

>>>>

    Another area of future work is the expansion of the SDLC-AE to include
    more artifacts of the SDLC.  The more artifacts and processes that can
    be collected, the deeper the understanding of the SDLC.  
    All of the data collection combined with better software analytics
    could lead to true \textit{data-driven software engineering}. Data-driven
    software engineering is the application of collecting and analyzing historical
    information about software engineering artifacts in order to
    accurately predict the outcomes of software engineering projects. This
    will lead to more informed decisions about software engineering.  Figure
    \ref{fig:sdlc-ae-adv} shows an expansion of the previous SDLC-AE diagram.  
    The new elements are in the unshaded boxes, and they are not exhaustive.
    Data-driven software engineering should 
    not to be confused with data-driven programming, in which the computer code
    describes the data instead of the sequence of opertions \cite{DDP2015}.

    \begin{figure}[ht]
    \includegraphics[scale=.75]{images/sdlcae-adv.png}
    \caption{SDLC ANALYTIC ENGINE EXPANSION}
    \label{fig:sdlc-ae-adv}
    \end{figure}

    Currently, CRI provides a single method to evaluate past 
    performance, but it does not
    provide any guidance around making more informed future decisions. 
    Some phases are not properly tracked with the initial SDLC-AE and more
    data can be tracked for the existing phases.
    Schedules for each of the individual phases of the SDLC need to be tracked,
    not just the entire project.  Teams need to know how much time is spent
    in design versus testing.  Also, how much time is required to generate
    proper test cases?  These are just a couple of examples of expansions
    to the SDLC-AE.  These and other advancements could lead to greater
    insights about SDLC phases that are struggling and need improvement.
    The SDLC-AE could be expanded to have predictive capabilities.
